---
title: "midterm project team 5"
output: html_document
date: "2022-10-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

install some packages or libraries
```{r}

library(ggplot2)
library(ezids)
library(dplyr)
library(readr)
```

## read data
Read the data .CSV files of adults arrest in DC area from 2016-2021
```{r }

df_2016<-data.frame(read.csv("Arrests 2016 Public.csv"))[,1:14]
df_2017<-data.frame(read.csv("Arrests 2017 Public.csv"))[,1:14]
df_2018<-data.frame(read.csv("Arrests by Year, 2018.csv"))[,1:14]
df_2019<-data.frame(read.csv("Arrests by Year, 2019.csv"))[,1:14]
df_2020<-data.frame(read.csv("Arrests by Year 2020.csv"))[,1:14]
df_2021<-data.frame(read.csv("2021 Adult Arrests.csv"))[,1:14]
```
Note that the colnames of df_2016 and df_2017 are not the same with others. But those indices are just about arrest location which is not what we are investigating. Therefore I just combined them by the same indices that we need. (A-N columns)
##Merge Multiple CSV Files
bind by rows

```{r}


DF<-rbind(df_2016,df_2017,df_2018,df_2019,df_2020,df_2021)
colnames(DF)
xkablesummary(DF)
```



## Including Plots



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


